PTFO 8-8695: Two Stars, Two Signals, No Planet

### 2020-05-12 paper/ms.tex
merge Dana Louie comments

% PENDING yy
\author{D. Louie} % danalouie@astro.umd.edu
\affiliation{University of Maryland, Baltimore County, 1000 Hilltop
Circle, Baltimore, MD 21250, USA}

@@

The periodogram of the final residual (Figures~\ref{fig:splitsignal}
and~\ref{fig:splitsignalii} bottom row) shows a barely significant and
poorly-resolved peak at $\approx$8 days, consistent with the visual
impression of some slower trends in the residuals after subtracting
the shorter- and longer-period signals.

@@

One particularly interesting feature of the dip is its epoch.  The
dips do not occur with strict periodicity \citep{yu_tests_2015}.  In
fact, \citet{tanimoto_evidence_2020} provided stark evidence for
different behavior altogether: over a time-span of years, the dip
``split'' into distinct groups at particular repeating phases.  See
for instance their Figures~2 through~4.  Fitting a decade of
observations, they provided the following linear ephemeris, which we
did not find any need to update.
\begin{align}
t_0\ {\rm BJD}_{\rm TDB} &= 2455543.943 \pm 0.002 \\
P &= 0.4483993 \pm 0.0000006 d.
\end{align}

Figure~\ref{fig:o_minus_c} shows the phase of the dip we detected in
the TESS data, relative to their ephemeris.  It agrees with the
independent December 2018 measurements by
\citet{tanimoto_evidence_2020}: either the dip abruptly shifted phase
over the past decade or, more likely, there are multiple dips that
have come and gone at different phases.

>>>>

% PENDING yy
\author[0000-0002-2457-272X]{D.~R.~Louie} % danalouie@astro.umd.edu
\affiliation{Department of Astronomy, University of Maryland, College
Park, MD 20742, USA}

@@

The periodogram of the final residual shows a barely significant and
poorly-resolved peak at $\approx$8 days, consistent with the visual
impression of some slower trends in the bottom rows of
Figures~\ref{fig:splitsignal} and~\ref{fig:splitsignalii}.

@@

One particularly interesting feature of the dip is its epoch.  The
dips do not occur with strict periodicity \citep{yu_tests_2015}.  In
fact, \citet{tanimoto_evidence_2020} provided stark evidence for
different behavior altogether: over a time-span of years, the dip
``split'' into distinct groups at particular repeating phases.  See
for instance their Figures~2 through~4.  Fitting a decade of
observations, they provided the following linear ephemeris, which we
did not find any need to update.
\begin{align}
t_0\ {\rm BJD}_{\rm TDB} &= 2455543.943 \pm 0.002 \nonumber \\
P &= 0.4483993 \pm 0.0000006\,{\rm d}.
\label{eq:ephem}
\end{align}

Figure~\ref{fig:o_minus_c} shows the observed mid-transit times of
dips minus the times predicted from Equation~\ref{eq:ephem}.  The
phase of the dip we detected in the TESS data (yellow star) agrees
with the independent December 2018 measurements by
\citet{tanimoto_evidence_2020}: either the dip abruptly shifted phase
over the past decade or, more likely, there are multiple dips that
have come and gone at different phases.
